### 2019-11-21 2_task_bench.tex
Fiddle with figure placement.
MPI code sample.
add a table to describe APIs of the core lib
Edit the introduction to make some points more clear.
Fiddle with figures.
Edits to section 2.

@@

@@

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the core library manages
parsing input parameters and displaying results,
ensuring that all implementations behave uniformly and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 15 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being
typical. Listings~\ref{lst:compute-kernel} and \ref{lst:code-sample}
show excerpts from the Task Bench core, and the Dask implementation,
respectively. Only the code in Listing~\ref{lst:code-sample} is
implemented for each system, minimizing the work required for each additional system.

\input{l0_compute_kernel}
\input{l1_code_sample}

>>>>

\brokenpenalty=0

@@

\brokenpenalty=\oldbrokenpenalty

@@

Listing~\ref{lst:code-sample} shows an excerpt from the Task Bench
implementation in MPI. Methods of the \lstinline{Graph} object
\lstinline{g} are provided by Task Bench's core API and are shared
among all implementations. These methods are summarized in
Table~\ref{tab:api}. The MPI implementation follows the style of
communicating sequential processes, and simply executes a set of send
and receive calls (lines 24 and 16, respectively) followed by
executing the task body (line 32). For simplicity, the excerpt
assumes the number of MPI ranks is equal to the width of the graph;
the full implementation is more general and provides additional
optimizations. Despite its simplicity, this MPI implementation is
among our best performing, and shows that Task Bench can be mapped to
idiomatic code even in programming systems with no native concept of
task.

In addition specifying the shape and structure of the task graph, the
Task Bench core API also provides implementations of the kernels
executed by each task as well as other utility routines (to parse
inputs and display results). A sample of the core API compute kernel
is shown in Listing~\ref{lst:compute-kernel}. In addition to reducing
the effort required to implement Task Bench, providing central
implementations of these services ensures that all Task Bench
implementations can be scripted uniformly and eliminates a potential
source of performance disparity that can be a pitfall for mini-apps.

%% (task(t,i) refers to the task at column i of timestep t)

\input{t3_api}
\input{l0_compute_kernel}
%% \input{l1_code_sample}
\input{l2_mpi_sample}

\zap{
Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the core library manages
parsing input parameters and displaying results,
ensuring that all implementations behave uniformly and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 15 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being
typical. Listings~\ref{lst:compute-kernel} and \ref{lst:code-sample}
show excerpts from the Task Bench core, and the Dask implementation,
respectively. Only the code in Listing~\ref{lst:code-sample} is
implemented for each system, minimizing the work required for each additional system.
} % zap
